---
title: "Phenotype_plots"
output: html_document
---

```{r LoadPackages and palettes, include=FALSE}
library(ggplot2)
library(ggpubr)
library(dplyr)

library(tidyverse)
# color palettes and files
cbbPalette <- c("#000000", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
set.seed(9297)
phenotype_results_sampling <- read.delim("Hub_Inocula_Fungi_map_update.txt")
phenotype_results_all <- read.delim("hub_inocula_above.txt")

```


These plots were made both by day an doverall to show the general trend of the tratments.
```{r Photosynq}
# phiNPQ

phenotype_results_all$Days_post_drought<- factor(phenotype_results_all$Days_post_drought,                                                           level=c("-2","0","2","4","6","8","10","12","14","16","18","20","22","24"))

phenotype_results_all_phiNPQ <- phenotype_results_all[!is.na(phenotype_results_all$PhiNPQ),]
phenotype_results_all_phiNPQ 
phiNPQ_plot_day <- ggplot(phenotype_results_all_phiNPQ, aes(x = Days_post_drought , y = PhiNPQ, color = Treatment, group = interaction(Treatment))) + 
  geom_jitter(shape=16, position=position_jitter(0.4), alpha=.3)+
  stat_summary(fun.y=mean,geom="line") +
  theme(legend.key.height = unit(0.15, "cm"), legend.key.width = unit(0.25, "cm")) +
  theme(legend.title = element_text(size = 8, face = "bold"), legend.text = element_text(size = 12)) +
  stat_summary(fun.data = mean_se, geom = "errorbar", width = 0.5) +
  ylab("PhiNPQ") + 
  scale_x_discrete("Days Post Drought",labels =c("0","2","4","6","8","10","12","14","16","18","20","22","24"))+
  xlab("Days Post Drought Start")+
  ggtitle("PhiNPQ - Daily") + 
  xlab("")+
  scale_color_manual(values=cbbPalette) +
  theme(
    strip.background = element_rect(color="white", fill="white", size=1.5, linetype="solid"))+
  #scale_linetype_manual(values = c(rep("solid", 2), rep("dashed", 2))) +
  stat_compare_means(method = "wilcox", aes(label = ..p.signif..), hide.ns = TRUE, size = 6, label.y = 0.77)+
  theme_classic()


phiNPQ_plot <- ggplot(phenotype_results_all_phiNPQ, aes(x = Treatment , y = PhiNPQ, color = Treatment)) + 
  stat_summary(fun.y=mean,geom="line") +
  theme(legend.key.height = unit(0.15, "cm"), legend.key.width = unit(0.25, "cm")) +
  theme(legend.title = element_text(size = 8, face = "bold"), legend.text = element_text(size = 12)) +
  stat_summary(fun.data = mean_se, geom = "errorbar", width = 0.5) +
  ylab("PhiNPQ") + 
  scale_x_discrete("Treatment",labels =c("Control","Experimental"))+
  xlab("Treatment")+
  ggtitle("PhiNPQ - Overall") + 
  xlab("")+
  geom_boxplot()+
  scale_color_manual(values=cbbPalette) +
  geom_jitter(shape=16, position=position_jitter(0.4), alpha=.3)+
  theme(
    strip.background = element_rect(color="white", fill="white", size=1.5, linetype="solid"))+
  #scale_linetype_manual(values = c(rep("solid", 2), rep("dashed", 2))) +
  stat_compare_means(method = "wilcox", aes(label = ..p.signif..), hide.ns = FALSE, size = 6, label.y = 0.75)+
  theme_classic()


phiNPQ_combo <- ggarrange(phiNPQ_plot_day,phiNPQ_plot, common.legend = TRUE)

# Phi2
phenotype_results_all_Phi2 <- phenotype_results_all[!is.na(phenotype_results_all$Phi2),]
phenotype_results_all_Phi2 
Phi2_plot_day <- ggplot(phenotype_results_all_Phi2, aes(x = Days_post_drought , y = Phi2, color = Treatment, group = interaction(Treatment))) + 
  geom_jitter(shape=16, position=position_jitter(0.4), alpha=.3)+
  stat_summary(fun.y=mean,geom="line") +
  theme(legend.key.height = unit(0.15, "cm"), legend.key.width = unit(0.25, "cm")) +
  theme(legend.title = element_text(size = 8, face = "bold"), legend.text = element_text(size = 12)) +
  stat_summary(fun.data = mean_se, geom = "errorbar", width = 0.5) +
  ylab("Phi2") + 
  scale_x_discrete("Days Post Drought",labels =c("0","2","4","6","8","10","12","14","16","18","20","22","24"))+
  xlab("Days Post Drought Start")+
  ggtitle("Phi2 - Daily") + 
  xlab("")+
  scale_color_manual(values=cbbPalette) +
  theme(
    strip.background = element_rect(color="white", fill="white", size=1.5, linetype="solid"))+
  #scale_linetype_manual(values = c(rep("solid", 2), rep("dashed", 2))) +
  stat_compare_means(method = "wilcox", aes(label = ..p.signif..), hide.ns = TRUE, size = 6, label.y = 0.6)+
  theme_classic()


Phi2_plot <- ggplot(phenotype_results_all_Phi2, aes(x = Treatment , y = Phi2, color = Treatment)) + 
  stat_summary(fun.y=mean,geom="line") +
  theme(legend.key.height = unit(0.15, "cm"), legend.key.width = unit(0.25, "cm")) +
  theme(legend.title = element_text(size = 8, face = "bold"), legend.text = element_text(size = 12)) +
  stat_summary(fun.data = mean_se, geom = "errorbar", width = 0.5) +
  ylab("Phi2") + 
  scale_x_discrete("Treatment",labels =c("Control","Experimental"))+
  xlab("Treatment")+
  ggtitle("Phi2 - Overall") + 
  xlab("")+
  geom_boxplot()+
  scale_color_manual(values=cbbPalette) +
  geom_jitter(shape=16, position=position_jitter(0.4), alpha=.3)+
  theme(
    strip.background = element_rect(color="white", fill="white", size=1.5, linetype="solid"))+
  #scale_linetype_manual(values = c(rep("solid", 2), rep("dashed", 2))) +
  stat_compare_means(method = "wilcox", aes(label = ..p.signif..), hide.ns = FALSE, size = 6, label.y = 0.6)+
  theme_classic()


Phi2_combo <- ggarrange(Phi2_plot_day,Phi2_plot, common.legend = TRUE)

# photosynthesis day by day plot
suppl_fig_1 <- ggarrange(Phi2_plot_day,phiNPQ_plot_day, common.legend =TRUE)

# LEF plots
phenotype_results_all_LEF <- phenotype_results_all[!is.na(phenotype_results_all$LEF),]
phenotype_results_all_LEF 
LEF_plot_day <- ggplot(phenotype_results_all_LEF, aes(x = Days_post_drought , y = LEF, color = Treatment, group = interaction(Treatment))) + 
  geom_jitter()+
  stat_summary(fun.y=mean,geom="line") +
  theme(legend.key.height = unit(0.15, "cm"), legend.key.width = unit(0.25, "cm")) +
  theme(legend.title = element_text(size = 8, face = "bold"), legend.text = element_text(size = 12)) +
  stat_summary(fun.data = mean_se, geom = "errorbar", width = 0.5) +
  ylab("LEF") + 
  scale_x_discrete("Days Post Drought",labels =c("0","2","4","6","8","10","12","14","16","18","20","22","24"))+
  xlab("Days Post Drought Start")+
  ggtitle("LEF - Daily") + 
  xlab("")+
  scale_color_manual(values=cbbPalette) +
  theme(
    strip.background = element_rect(color="white", fill="white", size=1.5, linetype="solid"))+
  #scale_linetype_manual(values = c(rep("solid", 2), rep("dashed", 2))) +
  stat_compare_means(method = "wilcox", aes(label = ..p.signif..), hide.ns = TRUE, size = 6, label.y = 150)+
  theme_classic()


LEF_plot <- ggplot(phenotype_results_all_LEF, aes(x = Treatment , y = LEF, color = Treatment)) + 
  stat_summary(fun.y=mean,geom="line") +
  theme(legend.key.height = unit(0.15, "cm"), legend.key.width = unit(0.25, "cm")) +
  theme(legend.title = element_text(size = 8, face = "bold"), legend.text = element_text(size = 12)) +
  stat_summary(fun.data = mean_se, geom = "errorbar", width = 0.5) +
  ylab("LEF") + 
  scale_x_discrete("Treatment",labels =c("Control","Experimental"))+
  xlab("Treatment")+
  ggtitle("LEF - Overall") + 
  xlab("")+
  geom_boxplot()+
  scale_color_manual(values=cbbPalette) +
  geom_jitter(shape=16, position=position_jitter(0.4), alpha=.3)+
  theme(
    strip.background = element_rect(color="white", fill="white", size=1.5, linetype="solid"))+
  #scale_linetype_manual(values = c(rep("solid", 2), rep("dashed", 2))) +
  stat_compare_means(method = "wilcox", aes(label = ..p.signif..), hide.ns = FALSE, size = 6, label.y = 0.9)+
  theme_classic()


LEF_combo <- ggarrange(LEF_plot_day,LEF_plot, common.legend = TRUE)

# PhiNO
phenotype_results_all_PhiNO <- phenotype_results_all[!is.na(phenotype_results_all$PhiNO),]
phenotype_results_all_PhiNO 
PhiNO_plot_day <- ggplot(phenotype_results_all_PhiNO, aes(x = Days_post_drought , y = PhiNO, color = Treatment, group = interaction(Treatment))) + 
  geom_jitter()+
  stat_summary(fun.y=mean,geom="line") +
  theme(legend.key.height = unit(0.15, "cm"), legend.key.width = unit(0.25, "cm")) +
  theme(legend.title = element_text(size = 8, face = "bold"), legend.text = element_text(size = 12)) +
  stat_summary(fun.data = mean_se, geom = "errorbar", width = 0.5) +
  ylab("PhiNO") + 
  scale_x_discrete("Days Post Drought",labels =c("0","2","4","6","8","10","12","14","16","18","20","22","24"))+
  xlab("Days Post Drought Start")+
  ggtitle("PhiNO - Daily") + 
  xlab("")+
  scale_color_manual(values=cbbPalette) +
  theme(
    strip.background = element_rect(color="white", fill="white", size=1.5, linetype="solid"))+
  #scale_linetype_manual(values = c(rep("solid", 2), rep("dashed", 2))) +
  stat_compare_means(method = "wilcox", aes(label = ..p.signif..), hide.ns = TRUE, size = 6, label.y = .35)+
  theme_classic()


PhiNO_plot <- ggplot(phenotype_results_all_PhiNO, aes(x = Treatment , y = PhiNO, color = Treatment)) + 
  stat_summary(fun.y=mean,geom="line") +
  theme(legend.key.height = unit(0.15, "cm"), legend.key.width = unit(0.25, "cm")) +
  theme(legend.title = element_text(size = 8, face = "bold"), legend.text = element_text(size = 12)) +
  stat_summary(fun.data = mean_se, geom = "errorbar", width = 0.5) +
  ylab("PhiNO") + 
  scale_x_discrete("Treatment",labels =c("Control","Experimental"))+
  xlab("Treatment")+
  ggtitle("PhiNO - Overall") + 
  xlab("")+
  geom_boxplot()+
  scale_color_manual(values=cbbPalette) +
  geom_jitter(shape=16, position=position_jitter(0.4), alpha=.3)+
  theme(
    strip.background = element_rect(color="white", fill="white", size=1.5, linetype="solid"))+
  #scale_linetype_manual(values = c(rep("solid", 2), rep("dashed", 2))) +
  stat_compare_means(method = "wilcox", aes(label = ..p.signif..), hide.ns = FALSE, size = 6, label.y = 0.35)+
  theme_classic()


PhiNO_combo <- ggarrange(PhiNO_plot_day,PhiNO_plot, common.legend = TRUE)
PhiNO_combo

# relative chlorophyll
phenotype_results_all_Relative_Chlorophyll <- phenotype_results_all[!is.na(phenotype_results_all$Relative_Chlorophyll),]
phenotype_results_all_Relative_Chlorophyll 
Relative_Chlorophyll_plot_day <- ggplot(phenotype_results_all_Relative_Chlorophyll, aes(x = Days_post_drought , y = Relative_Chlorophyll, color = Treatment, group = interaction(Treatment))) + 
  geom_jitter()+
  stat_summary(fun.y=mean,geom="line") +
  theme(legend.key.height = unit(0.15, "cm"), legend.key.width = unit(0.25, "cm")) +
  theme(legend.title = element_text(size = 8, face = "bold"), legend.text = element_text(size = 12)) +
  stat_summary(fun.data = mean_se, geom = "errorbar", width = 0.5) +
  ylab("Relative_Chlorophyll") + 
  scale_x_discrete("Days Post Drought",labels =c("0","2","4","6","8","10","12","14","16","18","20","22","24"))+
  xlab("Days Post Drought Start")+
  ggtitle("Relative_Chlorophyll - Daily") + 
  xlab("")+
  scale_color_manual(values=cbbPalette) +
  theme(
    strip.background = element_rect(color="white", fill="white", size=1.5, linetype="solid"))+
  #scale_linetype_manual(values = c(rep("solid", 2), rep("dashed", 2))) +
  stat_compare_means(method = "wilcox", aes(label = ..p.signif..), hide.ns = TRUE, size = 6, label.y = 60)+
  theme_classic()


Relative_Chlorophyll_plot <- ggplot(phenotype_results_all_Relative_Chlorophyll, aes(x = Treatment , y = Relative_Chlorophyll, color = Treatment)) + 
  stat_summary(fun.y=mean,geom="line") +
  theme(legend.key.height = unit(0.15, "cm"), legend.key.width = unit(0.25, "cm")) +
  theme(legend.title = element_text(size = 8, face = "bold"), legend.text = element_text(size = 12)) +
  stat_summary(fun.data = mean_se, geom = "errorbar", width = 0.5) +
  ylab("Relative_Chlorophyll") + 
  scale_x_discrete("Treatment",labels =c("Control","Experimental"))+
  xlab("Treatment")+
  ggtitle("Relative_Chlorophyll - Overall") + 
  xlab("")+
  geom_boxplot()+
  scale_color_manual(values=cbbPalette) +
  geom_jitter(shape=16, position=position_jitter(0.4), alpha=.3)+
  theme(
    strip.background = element_rect(color="white", fill="white", size=1.5, linetype="solid"))+
  #scale_linetype_manual(values = c(rep("solid", 2), rep("dashed", 2))) +
  stat_compare_means(method = "wilcox", aes(label = ..p.signif..), hide.ns = FALSE, size = 6, label.y = 51)+
  theme_classic()


Relative_Chlorophyll_combo <- ggarrange(Relative_Chlorophyll_plot_day,Relative_Chlorophyll_plot, common.legend = TRUE)



```






Aboveground area and biomass,done with the mapping file because these samples weretaken only at the five timepoints.Photos were not taken at T1, so area analysis is not available. 
```{r Aboveground}
# Area plot setup
phenotype_results_sampling_above <- phenotype_results_sampling[phenotype_results_sampling$Organ == "Leaves",]
phenotype_results_sampling_above_area <- phenotype_results_sampling_above
phenotype_results_sampling_above_area <- phenotype_results_sampling_above_area[!is.na(phenotype_results_sampling_above_area$above_area_cm2),]
phenotype_results_sampling_above_area$Timepoint <- factor(phenotype_results_sampling_above_area$Timepoint,
                                                            level=c("T2","T3","T4","T5"))
above_area_plot <- ggplot(phenotype_results_sampling_above_area, aes(x = Timepoint, y = above_area_cm2, color = Treatment, group = interaction(Treatment))) + 
  geom_jitter(shape=16, position=position_jitter(0.4), alpha=.3)+
  stat_summary(fun.y=mean,geom="line") +
  theme(legend.key.height = unit(0.15, "cm"), legend.key.width = unit(0.25, "cm")) +
  theme(legend.title = element_text(size = 8, face = "bold"), legend.text = element_text(size = 12)) +
  stat_summary(fun.data = mean_se, geom = "errorbar", width = 0.5) +
  ylab("Aboveground Plant Area (cm2)") + 
  scale_x_discrete("Timepoint",labels =c("T2","T3","T4","T5"))+
  xlab("Timepoint")+
  ggtitle("Aboveground Area") + 
  xlab("")+
  scale_color_manual(values=cbbPalette) +
  theme(
    strip.background = element_rect(color="white", fill="white", size=1.5, linetype="solid"))+
  #scale_linetype_manual(values = c(rep("solid", 2), rep("dashed", 2))) +
  stat_compare_means(method = "wilcox", aes(label = ..p.signif..), hide.ns = TRUE, size = 6, label.y = 73)+
  theme_classic()


# Above Biomass Plot Setup
phenotype_results_sampling_above_biomass <- phenotype_results_sampling_above
phenotype_results_sampling_above_biomass <- phenotype_results_sampling_above_biomass[!is.na(phenotype_results_sampling_above_biomass$above_biomass),]
phenotype_results_sampling_above_biomass$Timepoint <- factor(phenotype_results_sampling_above_biomass$Timepoint,
                                                            level=c("T1","T2","T3","T4","T5"))
above_biomass_plot <- ggplot(phenotype_results_sampling_above_biomass, aes(x = Timepoint, y = above_biomass, color = Treatment, group = interaction(Treatment))) + 
  geom_jitter(shape=16, position=position_jitter(0.4), alpha=.3)+
  stat_summary(fun.y=mean,geom="line") +
  theme(legend.key.height = unit(0.15, "cm"), legend.key.width = unit(0.25, "cm")) +
  theme(legend.title = element_text(size = 8, face = "bold"), legend.text = element_text(size = 12)) +
  stat_summary(fun.data = mean_se, geom = "errorbar", width = 0.5) +
  ylab("Aboveground Plant Biomass(mg)") + 
  scale_x_discrete("Timepoint",labels =c("T1","T2","T3","T4","T5"))+
  xlab("Timepoint")+
  ggtitle("Aboveground Biomass") + 
  xlab("")+
  scale_color_manual(values=cbbPalette) +
  theme(
    strip.background = element_rect(color="white", fill="white", size=1.5, linetype="solid"))+
  #scale_linetype_manual(values = c(rep("solid", 2), rep("dashed", 2))) +
  stat_compare_means(method = "wilcox", aes(label = ..p.signif..), hide.ns = TRUE, size = 6, label.y = 325)+
  theme_classic()

# plant height
phenotype_results_all$Days_post_drought <- factor(phenotype_results_all$Days_post_drought,
                                                            level=c("-2","0","2","4","6","8","10","12","14","16","18","20","22","24"))

phenotype_results_all <- phenotype_results_all[!is.na(phenotype_results_all$Days_post_drought),]

above_height_plot <- ggplot(phenotype_results_all, aes(x = Days_post_drought , y = Height_to_highest_node, color = Treatment, group = interaction(Treatment))) + 
  geom_jitter(shape=16, position=position_jitter(0.4), alpha=.3)+
  stat_summary(fun.y=mean,geom="line") +
  theme(legend.key.height = unit(0.15, "cm"), legend.key.width = unit(0.25, "cm")) +
  theme(legend.title = element_text(size = 8, face = "bold"), legend.text = element_text(size = 12)) +
  stat_summary(fun.data = mean_se, geom = "errorbar", width = 0.5) +
  ylab("Height to Highest Node (cm)") + 
  scale_x_discrete("Days Post Drought",labels =c("-2","0","2","4","6","8","10","12","14","16","18","20","22","24"))+
  xlab("Days Post Drought Start")+
  ggtitle("Height to Highest Node") + 
  xlab("")+
  scale_color_manual(values=cbbPalette) +
  theme(
    strip.background = element_rect(color="white", fill="white", size=1.5, linetype="solid"))+
  #scale_linetype_manual(values = c(rep("solid", 2), rep("dashed", 2))) +
  stat_compare_means(method = "wilcox", aes(label = ..p.signif..), hide.ns = TRUE, size = 6, label.y = 12)+
  theme_classic()

above_phenotypes_combo <- ggarrange(above_area_plot,above_biomass_plot,above_height_plot,Phi2_plot,phiNPQ_plot,ncol =5,common.legend = TRUE, legend ="bottom")
above_phenotypes_combo
```


Belowground plots, again performed with the mapping file as pictures only taken at molecular sampling points.
```{r Belowground}
phenotype_results_sampling_below <- phenotype_results_sampling[phenotype_results_sampling$Organ == "Roots",]
# root tips
phenotype_results_sampling_below_tips <- phenotype_results_sampling_below[!is.na(phenotype_results_sampling_below$Number.of.Root.Tips),]
phenotype_results_sampling_below_tips$Timepoint <- factor(phenotype_results_sampling_below_tips$Timepoint,
                                       level=c("T1","T2","T3","T4","T5"))
root_tips_plot <- ggplot(phenotype_results_sampling_below_tips, aes(x = Timepoint, y = Number.of.Root.Tips, color = Treatment, group = interaction(Treatment))) + 
  geom_jitter(shape=16, position=position_jitter(0.4), alpha=.3)+
  stat_summary(fun.y=mean,geom="line") +
  theme(legend.key.height = unit(0.15, "cm"), legend.key.width = unit(0.25, "cm")) +
  theme(legend.title = element_text(size = 8, face = "bold"), legend.text = element_text(size = 12)) +
  stat_summary(fun.data = mean_se, geom = "errorbar", width = 0.5) +
  ylab("Number of Root Tips") + 
  scale_x_discrete("Timepoint",labels =c("T1","T2","T3","T4","T5"))+
  xlab("Timepoint")+
  ggtitle("Root Tips") + 
  xlab("")+
  scale_color_manual(values=cbbPalette) +
  theme(
    strip.background = element_rect(color="white", fill="white", size=1.5, linetype="solid"))+
  #scale_linetype_manual(values = c(rep("solid", 2), rep("dashed", 2))) +
  stat_compare_means(method = "wilcox", aes(label = ..p.signif..), hide.ns = TRUE, size = 6, label.y = 375)+
  theme_classic()


# root length plot
phenotype_results_sampling_below_length <- phenotype_results_sampling_below[!is.na(phenotype_results_sampling_below$Total.Root.Length.mm),]
phenotype_results_sampling_below_length$Timepoint <- factor(phenotype_results_sampling_below_length$Timepoint,
                                       level=c("T1","T2","T3","T4","T5"))
root_length_total_plot <- ggplot(phenotype_results_sampling_below_length, aes(x = Timepoint, y = Total.Root.Length.mm, color = Treatment, group = interaction(Treatment))) + 
  geom_jitter(shape=16, position=position_jitter(0.4), alpha=.3)+
  stat_summary(fun.y=mean,geom="line") +
  theme(legend.key.height = unit(0.15, "cm"), legend.key.width = unit(0.25, "cm")) +
  theme(legend.title = element_text(size = 8, face = "bold"), legend.text = element_text(size = 12)) +
  stat_summary(fun.data = mean_se, geom = "errorbar", width = 0.5) +
  ylab("Total Root Length (mm)") + 
  scale_x_discrete("Timepoint",labels =c("T1","T2","T3","T4","T5"))+
  xlab("Timepoint")+
  ggtitle("Total Root Length") + 
  xlab("")+
  scale_color_manual(values=cbbPalette) +
  theme(
    strip.background = element_rect(color="white", fill="white", size=1.5, linetype="solid"))+
  #scale_linetype_manual(values = c(rep("solid", 2), rep("dashed", 2))) +
  stat_compare_means(method = "wilcox", aes(label = ..p.signif..), hide.ns = TRUE, size = 6, label.y = 1490)+
  theme_classic()

# average root diameter
phenotype_results_sampling_below_diameter <- phenotype_results_sampling_below[!is.na(phenotype_results_sampling_below$Average.Diameter.mm),]
phenotype_results_sampling_below_diameter$Timepoint <- factor(phenotype_results_sampling_below_diameter$Timepoint,
                                       level=c("T1","T2","T3","T4","T5"))


average_diameter_plot <- ggplot(phenotype_results_sampling_below_diameter, aes(x = Timepoint, y = Average.Diameter.mm, color = Treatment, group = interaction(Treatment))) + 
  geom_jitter(shape=16, position=position_jitter(0.4), alpha=.3)+
  stat_summary(fun.y=mean,geom="line") +
  theme(legend.key.height = unit(0.15, "cm"), legend.key.width = unit(0.25, "cm")) +
  theme(legend.title = element_text(size = 8, face = "bold"), legend.text = element_text(size = 12)) +
  stat_summary(fun.data = mean_se, geom = "errorbar", width = 0.5) +
  ylab("Average Root Diameter (mm)") + 
  scale_x_discrete("Timepoint",labels =c("T1","T2","T3","T4","T5"))+
  xlab("Timepoint")+
  ggtitle("Root Diameter") + 
  xlab("")+
  scale_color_manual(values=cbbPalette) +
  theme(
    strip.background = element_rect(color="white", fill="white", size=1.5, linetype="solid"))+
  #scale_linetype_manual(values = c(rep("solid", 2), rep("dashed", 2))) +
  stat_compare_means(method = "wilcox", aes(label = ..p.signif..), hide.ns = TRUE, size = 6, label.y = .1)+
  theme_classic()


# volume
phenotype_results_sampling_below_volume <- phenotype_results_sampling_below[!is.na(phenotype_results_sampling_below$Volume.mm3),]
phenotype_results_sampling_below_volume$Timepoint <- factor(phenotype_results_sampling_below_volume$Timepoint,
                                       level=c("T1","T2","T3","T4","T5"))


volume_plot <- ggplot(phenotype_results_sampling_below_volume, aes(x = Timepoint, y = Volume.mm3, color = Treatment, group = interaction(Treatment))) + 
  geom_jitter(shape=16, position=position_jitter(0.4), alpha=.3)+
  stat_summary(fun.y=mean,geom="line") +
  theme(legend.key.height = unit(0.15, "cm"), legend.key.width = unit(0.25, "cm")) +
  theme(legend.title = element_text(size = 8, face = "bold"), legend.text = element_text(size = 12)) +
  stat_summary(fun.data = mean_se, geom = "errorbar", width = 0.5) +
  ylab("Root Volume (mm^3)") + 
  scale_x_discrete("Timepoint",labels =c("T1","T2","T3","T4","T5"))+
  xlab("Timepoint")+
  ggtitle("Root Volume") + 
  xlab("")+
  scale_color_manual(values=cbbPalette) +
  theme(
    strip.background = element_rect(color="white", fill="white", size=1.5, linetype="solid"))+
  #scale_linetype_manual(values = c(rep("solid", 2), rep("dashed", 2))) +
  stat_compare_means(method = "wilcox", aes(label = ..p.signif..), hide.ns = TRUE, size = 6, label.y = 250)+
  theme_classic()

# nodule counts 
phenotype_results_sampling_below_nodules <- phenotype_results_sampling_below[!is.na(phenotype_results_sampling_below$nodule_count),]
phenotype_results_sampling_below_nodules$Timepoint <- factor(phenotype_results_sampling_below_nodules$Timepoint,
                                       level=c("T1","T2","T3","T4","T5"))
root_nodules_plot <- ggplot(phenotype_results_sampling_below_nodules, aes(x = Timepoint, y = nodule_count, color = Treatment, group = interaction(Treatment))) + 
  geom_jitter(shape=16, position=position_jitter(0.4), alpha=.3)+
  stat_summary(fun.y=mean,geom="line") +
  theme(legend.key.height = unit(0.15, "cm"), legend.key.width = unit(0.25, "cm")) +
  theme(legend.title = element_text(size = 8, face = "bold"), legend.text = element_text(size = 12)) +
  stat_summary(fun.data = mean_se, geom = "errorbar", width = 0.5) +
  ylab("Number of Nodules") + 
  scale_x_discrete("Timepoint",labels =c("T1","T2","T3","T4","T5"))+
  xlab("Timepoint")+
  ggtitle("") + 
  xlab("")+
  scale_color_manual(values=cbbPalette) +
  theme(
    strip.background = element_rect(color="white", fill="white", size=1.5, linetype="solid"))+
  #scale_linetype_manual(values = c(rep("solid", 2), rep("dashed", 2))) +
   ggtitle("Nodule Counts") +
  stat_compare_means(method = "wilcox", aes(label = ..p.signif..), hide.ns = TRUE, size = 6, label.y =15)+
  theme_classic()


root_plots_combo <- ggarrange(root_tips_plot,root_length_total_plot,average_diameter_plot,volume_plot, root_nodules_plot, ncol = 5,common.legend = TRUE, legend = "bottom")

root_plots_combo
```




```{r Follow up experiments - aboveground mass}

#well watered
well_watered_biomass <- read.csv("plant_weight_well_watered_31622.csv")


# stats added to plot outside of R
 stats <- compare_means(Weight ~ Type, data=well_watered_biomass, method="wilcox")
stats
write.csv(stats, file = "stats_check.csv")
well_watered_biomass_plot <- ggplot(well_watered_biomass, aes(x = Type, y = Weight, color = Genus)) + 
  geom_boxplot()+
  #stat_summary(fun.y=mean,geom="line") +
  theme(axis.text.x = element_blank())+
  theme(legend.key.height = unit(0.15, "cm"), legend.key.width = unit(0.25, "cm")) +
  theme(legend.title = element_text(size = 8, face = "bold"), legend.text = element_text(size = 12)) +
   geom_hline(yintercept = 177.8673913)+
  geom_hline(yintercept = 160.7727273, linetype =2)+
  #stat_summary(fun.data = mean_se, geom = "errorbar", width = 0.5) +
  ylab("Biomass (mg)") + 

  xlab("Treatment")+
  ggtitle("Well Watered Aboveground Biomass") + 
  xlab("")+
  geom_boxplot()+
  scale_color_manual(values=cbbPalette) +
  geom_jitter(shape=16, position=position_jitter(0.4))+
  theme(
    strip.background = element_rect(color="white", fill="white", size=1.5, linetype="solid"))+
  #stat_compare_means(comparisons = "my_comparisons")+
  theme_classic()
  #theme(axis.text.x = element_text(angle = -90))
well_watered_biomass_plot



# DROUGHT check
drought_biomass_check <- read.csv("drought_weights_32722_indiv.csv")
drought_biomass_check


# add stats to plot outside R
 stats_drought <- compare_means(Weight ~ Type, data=drought_biomass_check,method= "wilcox")

stats_drought
write.csv(stats_drought, file = "stats_check_drought.csv")
drought_biomass_plot <- ggplot(drought_biomass_check, aes(x = Type, y = Weight, color = Genus)) + 
  geom_boxplot()+
  #stat_summary(fun.y=mean,geom="line") +
  theme(axis.text.x = element_text(angle = 90))+
  theme(legend.key.height = unit(0.15, "cm"), legend.key.width = unit(0.25, "cm")) +
  theme(legend.title = element_text(size = 8, face = "bold"), legend.text = element_text(size = 12)) +
   geom_hline(yintercept = 175.8488889)+
  geom_hline(yintercept = 157.3818182, linetype =2)+
  #stat_summary(fun.data = mean_se, geom = "errorbar", width = 0.5) +
  ylab("Biomass (mg)") + 

  xlab("Treatment")+
  ggtitle("Low-Moisture Aboveground Biomass") + 
  xlab("")+
  geom_boxplot()+
  scale_color_manual(values=cbbPalette) +
  geom_jitter(shape=16, position=position_jitter(0.4))+
  theme(
    strip.background = element_rect(color="white", fill="white", size=1.5, linetype="solid"))+
  #stat_compare_means(comparisons = "my_comparisons")+
  theme_classic()+
  theme(axis.text.x = element_text(angle = -90))

drought_biomass_plot

```